---
title: "Main Data Differential Methylation Analysis"
author: "Aaron Kovacs"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
theme: cosmo
---

Testing code chunk

```{r, test}
library(dmrseq)
getwd()
Test1 <- read.table("meth_data/test-R1.bam.vcf.gz.cg.bed.gz")
Test2 <- head(Test1,50)
Test3 <- head(Test1,25)
Mvalues1 <- Test1$V4 * Test1$V5
str(as.matrix(Mvalues1))


MvaluesRounded1 <- round(Mvalues1)
str(Test1$V1)
str(Test1$V2)
str(Test1$V3)
str(Test1$V4)
str(Test1$V5)
str(Mvalues1)


str(as.matrix(Test1$V5))


bstest1 <- BSseq(chr = Test1$V1, pos = Test1$V2,
            M = as.matrix(Mvalues1), Cov = as.matrix(Test1$V5),
            sampleNames = "test1")

Mvalues2 <- Test2$V4 * Test2$V5
str(Mvalues2)
str(as.matrix(Mvalues2))

bstest2 <- BSseq(chr = Test2$V1, pos = Test2$V2,
            M = as.matrix(Mvalues2), Cov = as.matrix(Test2$V5),
            sampleNames = "test2")

Mvalues3 <- Test3$V4 * Test3$V5


bstest3 <- BSseq(chr = Test3$V1, pos = Test3$V2,
            M = as.matrix(Mvalues3), Cov = as.matrix(Test3$V5),
            sampleNames = "test3")


str(bstest2)
str(bstest1)

Testcomb <- combine(bstest1, bstest2, bstest3)
str(Testcomb)
show(Testcomb)
empty.loci.idx.test <- which(DelayedMatrixStats::rowSums2(getCoverage(Testcomb, type="Cov")==0)==0)
Testcomb.filtered <- Testcomb[empty.loci.idx.test]
```



```{r, ClearR1}
ClearR1 <- read.table("meth_data/Clear2F-R1.bam.vcf.gz.cg.bed.gz")
MvaluesC1 <- ClearR1$V4 * ClearR1$V5
bsClearR1 <- BSseq(chr = ClearR1$V1, pos = ClearR1$V2,
            M = as.matrix(MvaluesC1), Cov = as.matrix(ClearR1$V5),
            sampleNames = "ClearR1")
```



```{r, ClearR2}
ClearR2 <- read.table("meth_data/Clear2F-R2.bam.vcf.gz.cg.bed.gz")
MvaluesC2 <- ClearR2$V4 * ClearR2$V5
bsClearR2 <- BSseq(chr = ClearR2$V1, pos = ClearR2$V2,
            M = as.matrix(MvaluesC2), Cov = as.matrix(ClearR2$V5),
            sampleNames = "ClearR2")
```



```{r, ClearR3}
ClearR3 <- read.table("meth_data/Clear2F-R3.bam.vcf.gz.cg.bed.gz")
MvaluesC3 <- ClearR3$V4 * ClearR3$V5
bsClearR3 <- BSseq(chr = ClearR3$V1, pos = ClearR3$V2,
            M = as.matrix(MvaluesC3), Cov = as.matrix(ClearR3$V5),
            sampleNames = "ClearR3")
```



```{r, Foundation}
Foundation <- read.table("meth_data/Foundation.bam.vcf.gz.cg.bed.gz")
MvaluesF <- Foundation$V4 * Foundation$V5
MvaluesF1 <- MvaluesF / 2
MvaluesF2 <- MvaluesF / 2
CovF1 <- Foundation$V5 / 2
CovF2 <- Foundation$V5 / 2
bsFoundation1 <- BSseq(chr = Foundation$V1, pos = Foundation$V2,
            M = as.matrix(MvaluesF1), Cov = as.matrix(CovF1),
            sampleNames = "Foundation1")

bsFoundation2 <- BSseq(chr = Foundation$V1, pos = Foundation$V2,
            M = as.matrix(MvaluesF2), Cov = as.matrix(CovF2),
            sampleNames = "Foundation2")
```



```{r, GreenR1}
GreenR1 <- read.table("meth_data/Green3F-R1.bam.vcf.gz.cg.bed.gz")
MvaluesG1 <- GreenR1$V4 * GreenR1$V5
bsGreenR1 <- BSseq(chr = GreenR1$V1, pos = GreenR1$V2,
            M = as.matrix(MvaluesG1), Cov = as.matrix(GreenR1$V5),
            sampleNames = "GreenR1")
```


```{r, GreenR2}
GreenR2 <- read.table("meth_data/Green3F-R2.bam.vcf.gz.cg.bed.gz")
MvaluesG2 <- GreenR2$V4 * GreenR2$V5
bsGreenR2 <- BSseq(chr = GreenR2$V1, pos = GreenR2$V2,
            M = as.matrix(MvaluesG2), Cov = as.matrix(GreenR2$V5),
            sampleNames = "GreenR2")
```


```{r, GreenR3}
GreenR3 <- read.table("meth_data/Green3F-R3.bam.vcf.gz.cg.bed.gz")
MvaluesG3 <- GreenR3$V4 * GreenR3$V5
bsGreenR3 <- BSseq(chr = GreenR3$V1, pos = GreenR3$V2,
            M = as.matrix(MvaluesG3), Cov = as.matrix(GreenR3$V5),
            sampleNames = "GreenR3")
```



```{r, LilacR1}
LilacR1 <- read.table("meth_data/Lilac4F-R1.bam.vcf.gz.cg.bed.gz")
MvaluesL1 <- LilacR1$V4 * LilacR1$V5
bsLilacR1 <- BSseq(chr = LilacR1$V1, pos = LilacR1$V2,
            M = as.matrix(MvaluesL1), Cov = as.matrix(LilacR1$V5),
            sampleNames = "LilacR1")
```


```{r, LilacR2}
LilacR2 <- read.table("meth_data/Lilac4F-R2.bam.vcf.gz.cg.bed.gz")
MvaluesL2 <- LilacR2$V4 * LilacR2$V5
bsLilacR2 <- BSseq(chr = LilacR2$V1, pos = LilacR2$V2,
            M = as.matrix(MvaluesL2), Cov = as.matrix(LilacR2$V5),
            sampleNames = "LilacR2")
```


```{r, LilacR3}
LilacR3 <- read.table("meth_data/Lilac4F-R3.bam.vcf.gz.cg.bed.gz")
MvaluesL3 <- LilacR3$V4 * LilacR3$V5
bsLilacR3 <- BSseq(chr = LilacR3$V1, pos = LilacR3$V2,
            M = as.matrix(MvaluesL3), Cov = as.matrix(LilacR3$V5),
            sampleNames = "LilacR3")
```



```{r, Combine BSseq Objects}
bsdmrseq <- combine(bsClearR1, bsClearR2)
empty.loci.idx <- which(DelayedMatrixStats::rowSums2(getCoverage(bsdmrseq, type="Cov")==0)==0)
bsdmrseq <- bsdmrseq[empty.loci.idx]
bsdmrseq <- combine(bsdmrseq, bsClearR3) 
empty.loci.idx2 <- which(DelayedMatrixStats::rowSums2(getCoverage(bsdmrseq, type="Cov")==0)==0)
bsdmrseq <- bsdmrseq[empty.loci.idx2]
bsdmrseq <- combine(bsdmrseq, bsFoundation1)
empty.loci.idx3 <- which(DelayedMatrixStats::rowSums2(getCoverage(bsdmrseq, type="Cov")==0)==0)
bsdmrseq <- bsdmrseq[empty.loci.idx3]
bsdmrseq <- combine(bsdmrseq, bsFoundation2)
empty.loci.idx4 <- which(DelayedMatrixStats::rowSums2(getCoverage(bsdmrseq, type="Cov")==0)==0)
bsdmrseq <- bsdmrseq[empty.loci.idx4]
bsdmrseq <- combine(bsdmrseq, bsGreenR1)
empty.loci.idx5 <- which(DelayedMatrixStats::rowSums2(getCoverage(bsdmrseq, type="Cov")==0)==0)
bsdmrseq <- bsdmrseq[empty.loci.idx5]
bsdmrseq <- combine(bsdmrseq, bsGreenR2)
empty.loci.idx6 <- which(DelayedMatrixStats::rowSums2(getCoverage(bsdmrseq, type="Cov")==0)==0)
bsdmrseq <- bsdmrseq[empty.loci.idx6]
bsdmrseq <- combine(bsdmrseq, bsGreenR3)
empty.loci.idx7 <- which(DelayedMatrixStats::rowSums2(getCoverage(bsdmrseq, type="Cov")==0)==0)
bsdmrseq <- bsdmrseq[empty.loci.idx7]
bsdmrseq <- combine(bsdmrseq, bsLilacR1)
empty.loci.idx8 <- which(DelayedMatrixStats::rowSums2(getCoverage(bsdmrseq, type="Cov")==0)==0)
bsdmrseq <- bsdmrseq[empty.loci.idx8]
bsdmrseq <- combine(bsdmrseq, bsLilacR2)
empty.loci.idx9 <- which(DelayedMatrixStats::rowSums2(getCoverage(bsdmrseq, type="Cov")==0)==0)
bsdmrseq <- bsdmrseq[empty.loci.idx9]
bsdmrseq <- combine(bsdmrseq, bsLilacR3)
empty.loci.idx10 <- which(DelayedMatrixStats::rowSums2(getCoverage(bsdmrseq, type="Cov")==0)==0)
bsdmrseq.filtered <- bsdmrseq[empty.loci.idx10]
```

bsdmrseq <- combine(bsClearR1, bsClearR2, bsClearR3, bsFoundation1, bsFoundation2, bsGreenR1, bsGreenR2, bsGreenR3, bsLilacR1, bsLilacR2, bsLilacR3)



bsdmrseq <- combine(bsClearR1, bsClearR2)
bsdmrseq <- combine(bsdmrseq, bsClearR3) 
bsdmrseq <- combine(bsdmrseq, bsFoundation1)
bsdmrseq <- combine(bsdmrseq, bsFoundation2)
bsdmrseq <- combine(bsdmrseq, bsGreenR1)
bsdmrseq <- combine(bsdmrseq, bsGreenR2)
bsdmrseq <- combine(bsdmrseq, bsGreenR3)
bsdmrseq <- combine(bsdmrseq, bsLilacR1)
bsdmrseq <- combine(bsdmrseq, bsLilacR2)
bsdmrseq <- combine(bsdmrseq, bsLilacR3)