---
title: "Methylation Main Data QC Analysis"
author: "Aaron Kovacs & Mark Ziemann"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
theme: cosmo
---

This code is available at https://github.com/aaronsk7/guppy-methylation


This script performs differential methylation analysis using MethylKit.

```{r, libs,fig.height=8,fig.width=8}

library("R.utils")
library("parallel")

library("reshape2")
library("kableExtra")
library("dplyr")
library("RColorBrewer")
library("GenomicRanges")
library("limma")
library("methylKit")
library("gplots")
library("seqinr")

```


## Import biscuit data with a function

Define and test the function

```{r, importdata}

vcfz <- "meth_data/test-R1.bam.vcf.gz.cg.bed.gz"

biscuit2methylkit <- function(vcfz) {
vcf <- gsub(".gz$","",vcfz)
gunzip(vcfz)
tdata <- read.table(vcf)
gzip(vcf)
chrBase <- paste(tdata$V1,tdata$V2,sep=".")
chr <- tdata$V1
base <- tdata$V2
strand="F"
coverage <- tdata$V5
freqC <- tdata$V4 *100 
freqT <- 100-freqC 
mk <- data.frame(  chrBase , chr , base, strand,  coverage, freqC, freqT )
mk
mkname <- paste(vcf,".mk",sep="")
mkname <- gsub(".bam.vcf.gz.cg.bed","",mkname)
write.table(mk,file=mkname,quote=FALSE,sep="\t",row.names = FALSE)
}


biscuit2methylkit(vcfz)
getwd()
myobj=methRead("meth_data/test-R1.mk",
           sample.id="test1",
           assembly="hg18",
           treatment=1,
           context="CpG",
           mincov = 10 )
myobj


```

## Now format all the data into methylkit format

This might take a few minutes - get a cuppa.

```{r,bigimport}

basenames <- c("Clear2F-R1","Clear2F-R2","Clear2F-R3","Foundation","Green3F-R1","Green3F-R2","Green3F-R3",
               "Lilac4F-R1","Lilac4F-R2","Lilac4F-R3")
for (i in basenames){
  bedgz <- gsub("$","\\.bam\\.vcf\\.gz\\.cg\\.bed\\.gz",i)
  bedgz <- paste("meth_data/",bedgz,sep = "")
  mk <- gsub("$","\\.mk",i)
  mk <- paste("meth_data/",mk,sep = "")
  message(mk)
  if(file.exists(mk)){
    message(paste(mk,"exists"))
  }else{
    biscuit2methylkit(vcfz = bedgz)  
    }
  }
myfiles2 <- list.files("meth_data",pattern = "mk$",full.names = TRUE)
myfiles2

clrgrn <- as.list(myfiles2[c(grep("Clear",myfiles2) , grep("Lilac",myfiles2))])
clrgrn

myobj <-  methRead(clrgrn,
           sample.id = list("clear1","clear2","clear3","lilac1","lilac2","lilac3"),
           assembly = "hg19",
           treatment = c(0,0,0,1,1,1),
           context = "CpG",
           mincov = 3 )


```

## Simple stats

And prepare for differential methylation analysis.

```{r,fig.height=8,fig.width=8}

lapply(myobj,function(x){
  getMethylationStats(x,plot=FALSE,both.strands=FALSE)
  getMethylationStats(x,plot=TRUE,both.strands=FALSE)
  getCoverageStats(x,plot=TRUE,both.strands=FALSE)
})

myobj <- filterByCoverage(myobj,lo.count=1,lo.perc=NULL,
                                      hi.count=NULL,hi.perc=99.9)
tiles <- tileMethylCounts(myobj,win.size=1000,step.size=1000,cov.bases = 10)
meth <- unite(myobj, destrand=FALSE)
remove(myobj)
head(meth)

# plots
getCorrelation(meth,plot=TRUE)
clusterSamples(meth, dist="correlation", method="ward", plot=TRUE)
hc = clusterSamples(meth, dist="correlation", method="ward", plot=FALSE)
PCASamples(meth, screeplot=TRUE)
PCASamples(meth)

```


## Differential methylation


```{r,diffmeth}

myDiff <- calculateDiffMeth(meth)

# get hyper methylated bases
myDiff25p.hyper <- getMethylDiff(myDiff,difference=5,qvalue=0.01,type="hyper")

# get hypo methylated bases
myDiff25p.hypo <- getMethylDiff(myDiff,difference=5,qvalue=0.01,type="hypo")

# save object for later
saveRDS(object=myDiff,file="CvL_mydiff.rds",compress="gzip")

```


## Perform differential methylation on aggregated to 1kbp tiles

```{r,tiles1, fig.height=7,fig.height=7}

tiles <- unite(tiles, destrand=FALSE)

myDiff <- calculateDiffMeth(tiles)

# get hyper methylated bases
myDiff25p.hyper <- getMethylDiff(myDiff,difference=5,qvalue=0.01,type="hyper")

# get hypo methylated bases
myDiff25p.hypo <- getMethylDiff(myDiff,difference=5,qvalue=0.01,type="hypo")

# save object for later
saveRDS(object=myDiff,file="CvL_tiles_mydiff.rds",compress="gzip")


```


## Session information


For reproducibility.

```{r,sessioninfo}
sessionInfo()
```
